### 2014-11-09 tex/definitions.tex
Locked math. Switch to paper

@@

\begin{definition}
The universe of reachable states is $S$. The universe is further partitioned into states that activate different rules.
\begin{itemize}
\item Field Access, $S_\mathit{FA} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}\ (\cfgnt{e} = \cfgnt{r}) \wedge \exists \cfgnt{f},\cfgnt{k}_0\ (\cfgnt{k} = \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}_0\rp) \}$
\item Field Write,  $S_\mathit{FW} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}\ (\cfgnt{e} = \cfgnt{r}) \wedge \exists \cfgnt{x},\cfgnt{f},\cfgnt{k}_0\ (\cfgnt{k} = \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}_0\rp) \}$
\item Equals, $S_\mathit{EQ} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}_0 (\cfgnt{e} = \cfgnt{r}_0) \wedge \exists r_1, k_1(\cfgnt{k} = \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}_1\rp \}$
\item New, $S_\mathit{N} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{C}\ (\cfgnt{e} = \lp \cfgt{new}\ \cfgnt{C}\rp) \}$
\end{itemize} 
\end{definition}

@@

\begin{definition}
\label{def:hc}
Given the homomorphism $(\cfgnt{L}_p\ \cfgnt{R}_p) \rightharpoonup_{h} (\cfgnt{L}_q\ \cfgnt{R}_q)$, the \textbf{homomorphism constraint} $\mathbb{HC}((\cfgnt{L}_p\ \cfgnt{R}_p) \rightharpoonup_{h} (\cfgnt{L}_q\ \cfgnt{R}_q))$ is defined as:
\begin{align*}
\mathbb{HC}((\cfgnt{L}_p\ \cfgnt{R}_p) \rightharpoonup_{h} (\cfgnt{L}_q\ \cfgnt{R}_q)) &= \\
 \bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_p^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_q^\rightarrow)\} 
\end{align*}
\end{definition}

@@

\begin{definition}
\label{representation}
The \textbf{representation relation} $\sqsubset$ is defined as
follows: given state $s_p = (
\cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$
and state $s_q = (
\cfgnt{L}_q\ \cfgnt{R}_q\ \phi_q\ \eta_q\ \cfgnt{e}_q\ \cfgnt{k}_q )$,
$s_p \sqsubset s_q $ if and only if $\eta_p = \eta_q ,\ \cfgnt{e}_p =
\cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, and there exists a
homomorphism $(\cfgnt{L}_p\ \cfgnt{R}_p) \rightharpoonup_{h}
(\cfgnt{L}_q\ \cfgnt{R}_q)$ such that
\begin{equation}
\label{eqn:valid}
 \mathbb{S}( \phi_q \wedge \mathbb{HC}(s_p \rightharpoonup_{h} s_q) ) 
\end{equation}
The represented relation is extended to sets of states $P$ and $Q$ as
$$
P \sqsubset Q \Longleftrightarrow \forall q \in Q\ (\forall p \in S\ (p \sqsubset q \Rightarrow p \in P))
$$
\end{definition}

\begin{definition}
A state relation $p \rightarrow_x q$ is extended to sets of states $P \hookrightarrow_x Q$ as
$$
P \hookrightarrow_x Q \Longleftrightarrow \forall q \in S\ (p \rightarrow_x q \Rightarrow q \in Q)
$$
The $\rgse$ relations over sets of states is The $\rsym$ relation extended to sets of states
\end{definition}

\begin{definition}
\label{bisimulation}
The functional associated to bisimulation,  $F_\sim(\sqsubset)$, is the set of all pairs of sets of states
$(P\ Q)$ such that
\begin{equation}
\label{eqn:BisimulationForwards}
\forall p \in P\ (\forall p^\prime\ ( p \rgse p^\prime \Rightarrow \exists q^\prime\ ( (q \rsym q^\prime )\wedge (p^\prime\ \sqsubset\ q^\prime ))))
\end{equation}
\begin{equation}
\label{eqn:BisimulationBackwards}
\forall q \in Q\ (\forall q^\prime\ ( q \rsym q^\prime\Rightarrow \exists p^\prime\ ( (p \rgse p^\prime )\wedge (p^\prime\ \sqsubset\ q^\prime ))))
\end{equation}
The bisimularity relation is the greatest fixed point of the functional.
\end{definition}

>>>>

\begin{definition}
A state is \textbf{well formed} if its heap is deterministic, type consistent across locations on a common reference, every reference points to a location, and only references from the stack partition are in the environment, expression, or continuation.
\end{definition}

\begin{lemma}[Successors of well-formed states]
\label{lem:succ}
Any well-formed state has at least one successor unless the expression is $\cfgnt{v}$ and the continuation is $\cfgt{end}$.
\end{lemma}
\begin{proof}
Please write me!
\end{proof}

@@

\begin{definition}
The universe of reachable states is $S$. The universe is further partitioned into states that activate different relations.
\begin{itemize}
\item Field Access, $S_\mathit{FA} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}\ (\cfgnt{e} = \cfgnt{r}) \wedge \exists \cfgnt{f},\cfgnt{k}_0\ (\cfgnt{k} = \lp \cfgt{*}\ \cfgt{\$}\ \cfgnt{f} \rightarrow \cfgnt{k}_0\rp) \}$
\item Field Write,  $S_\mathit{FW} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}\ (\cfgnt{e} = \cfgnt{r}) \wedge \exists \cfgnt{x},\cfgnt{f},\cfgnt{k}_0\ (\cfgnt{k} = \lp \cfgnt{x}\ \cfgt{\$}\ \cfgnt{f}\ \cfgt{:=}\ \cfgt{*}\ \rightarrow\ \cfgnt{k}_0\rp) \}$
\item Equals, $S_\mathit{EQ} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{r}_0 (\cfgnt{e} = \cfgnt{r}_0) \wedge \exists r_1, k_1(\cfgnt{k} = \lp \cfgnt{r}_1\; \cfgt{=}\; \cfgt{*} \rightarrow \cfgnt{k}_1\rp \}$
\item New, $S_\mathit{N} = \{\lp \cfgnt{L}\ \cfgnt{R}\ \phi\ \eta\ \cfgnt{e}\ \cfgnt{k} \rp \in S \mid \exists \cfgnt{C}\ (\cfgnt{e} = \lp \cfgt{new}\ \cfgnt{C}\rp) \}$
\end{itemize} 
\end{definition}

@@

\begin{definition}
\label{def:hc}
Given the homomorphism $s_p \rightharpoonup_{h} s_q$, the \textbf{homomorphism constraint} $\mathbb{HC}(s_p \rightharpoonup_{h} s_q)$ is defined as:
\begin{align*}
\mathbb{HC}(s_p \rightharpoonup_{h} s_q) &= \\
 \bigwedge \{ \phi_b\ | \exists (\phi_a\ l) \in \cfgnt{L}_p^\rightarrow ( (\phi_b\ h(l)) \in \cfgnt{L}_q^\rightarrow)\} 
\end{align*}
Where $\cfgnt{L}_p$ and $\cfgnt{L}_q$ are the locations maps from the heaps in $s_p$ and $s_q$.
\end{definition}

@@

\begin{definition}
\label{representation}
The \textbf{representation relation} $\sqsubset$ is defined as
follows: given state $s_p = (
\cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$
and state $s_q = (
\cfgnt{L}_q\ \cfgnt{R}_q\ \phi_q\ \eta_q\ \cfgnt{e}_q\ \cfgnt{k}_q )$,
$s_p \sqsubset s_q $ if and only if $\eta_p = \eta_q ,\ \cfgnt{e}_p =
\cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, the heaps are well-formed, and there exists a
homomorphism $(\cfgnt{L}_p\ \cfgnt{R}_p) \rightharpoonup_{h}
(\cfgnt{L}_q\ \cfgnt{R}_q)$ such that
\begin{equation}
\label{eqn:valid}
 \mathbb{S}( \phi_q \wedge \mathbb{HC}(s_p \rightharpoonup_{h} s_q) ) 
\end{equation}
The represented relation is extended to sets of states $P$ and $Q$ as
$$
P \sqsubset Q \Longleftrightarrow \forall q \in Q\ (\forall p\ (p \sqsubset q \Rightarrow p \in P))
$$
\end{definition}

\begin{lemma}[$Q$ is a singleton for $P \sqsubset Q$]
\label{lem:unique}
$$
P \sqsubset Q \Rightarrow \forall q,q^\prime \in Q\ (\forall p\ (p \sqsubset q \Rightarrow p \sqsubset q^\prime)
$$
The notation $P \sqsubset q$ is used to indicate that single member of
the set in the represented relation.
\end{lemma}
\begin{proof}
Please write me?
\end{proof}
\begin{definition}
\label{def:meta}
A state relation $p \rightarrow_x p^\prime$ is extended to sets of states $P \hookrightarrow_x P^\prime$ as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
$$
The $\rgse$ relation over sets of states is $\rsgse = \hookrightarrow_\mathit{FA} \cup \hookrightarrow_\mathit{FA(N)} \cup \hookrightarrow_\mathit{FW} \cup \hookrightarrow_\mathit{FW(N)} \cup \hookrightarrow_\mathit{EQ(T)} \cup \hookrightarrow_\mathit{EQ(F)} \cup \hookrightarrow_\com$.%, and 
%the $\rsym$ relation extended to sets of states is 
%$$
%\rssym = \hookrightarrow_\mathit{FA} \cup \hookrightarrow_\mathit{FW} \cup \hookrightarrow_\mathit{EQ}^T \cup \hookrightarrow_\mathit{EQ}^F \cup \hookrightarrow_\com
%$$
\end{definition}

\begin{lemma}[$P$ and $Q$ have same number of successors when $P \sqsubset q$]
\label{lem:succCount}
Let $X = \{P^\prime | P \leadsto P^\prime\}$ and $Y = \{q^\prime | q
\rsym q^\prime\}$: $P \sqsubset q \Rightarrow |X| = |Y|$.
\end{lemma}
\begin{proof}
Please write me?
\end{proof}

\begin{definition}
\label{bisimulation}
The functional associated to bisimulation,  $F_\sim$, is a function between binary relations. The functional applied to $\sqsubset$, denoted as $F_\sim(\sqsubset)$, is the set of all pairs
$(P\ q)$ such that
\begin{equation}
\label{eqn:BisimulationForwards}
\forall P^\prime\ ( P \rsgse P^\prime \Rightarrow \exists q^\prime\ ( (q \rsym q^\prime )\wedge (P^\prime\ \sqsubset\ q^\prime )))
\end{equation}
\begin{equation}
\label{eqn:BisimulationBackwards}
\forall q^\prime\ ( q \rsym q^\prime\Rightarrow \exists P^\prime\ ( (P \rsgse P^\prime )\wedge (P^\prime\ \sqsubset\ q^\prime )))
\end{equation}
The bisimularity relation is the greatest fixed point of the functional.
\end{definition}
